Comparing and combining network-guided biomarker discovery to discover genetic susceptibility mechanisms to breast cancer on the GENESIS study

### 2020-10-07 manuscript/plos/review_1.tex
added diff file

\item[{heinz}] The goal of heinz is to identify the highest-scored connected subnetwork \cite{dittrich_identifying_2008}. The authors propose a transformation of the genes’ P\=value into a score that is negative under weak association with the phenotype, and positive under a strong one. This transformation is achieved by modeling the distribution of P\=/values by a beta-uniform model (BUM) parameterized by the desired false discovery rate (FDR). Thus formulated, the problem is NP-complete, and hence solving it would require a prohibitively long computational time. To solve it efficiently it is re-cast as the Prize-Collecting Steiner Tree Problem (PCST), which seeks to select the connected subnetwork S that maximizes the \emph{profit} p(S), defined as:

@@

Summary statistics for SNPs and genes are available at \url{https://github.com/hclimente/genewa}. We cannot share genotype data publicly for confidentiality reasons, but are available from GENESIS. Interested researchers can contact \href{mailto:nadine.andrieu@curie.fr}{nadine.andrieu@curie.fr}.

>>>>

\item[{heinz}] The goal of heinz is to identify the highest-scored connected subnetwork \cite{dittrich_identifying_2008}. The authors propose a transformation of the genes' P\=value into a score that is negative under weak association with the phenotype, and positive under a strong one. This transformation is achieved by modeling the distribution of P\=/values by a beta-uniform model (BUM) parameterized by the desired false discovery rate (FDR). Thus formulated, the problem is NP-complete, and hence solving it would require a prohibitively long computational time. To solve it efficiently it is re-cast as the Prize-Collecting Steiner Tree Problem (PCST), which seeks to select the connected subnetwork S that maximizes the \emph{profit} p(S), defined as:

@@

Summary statistics for SNPs and genes are available at \url{https://github.com/hclimente/genewa}. We cannot share genotype data publicly for confidentiality reasons, but are available from GENESIS. Interested researchers can contact \href{mailto:nadine.andrieu@curie.fr}{nadine.andrieu(at)curie.fr}.
